\textsf{Are large language models superhuman chemists?}

### 2024-10-07 src/tex/ms.tex
add statistics about number of questions
automatically vs. manually
rebuild from scratch

In this work, we report a novel benchmarking framework  (\Cref{fig:overview_figure}), which we call \chembench, and use it to reveal limitations of current frontier models for use in the chemical sciences.
%Our benchmark consists of \variable{output/total_number_of_questions.txt}\xspace question-answer pairs manually (\variable{output/manually_generated.txt}\unskip) or semi-automatically (\variable{output/automatically_generated.txt}\unskip) compiled from diverse sources.
Our corpus covers a large fraction of the topics taught in undergraduate and graduate chemistry curricula. It can be used to evaluate any system that can return text (i.e., including tool-augmented systems).

@@

@@

In addition, we thank the OpenBioML.org community and their ChemNLP project team for valuable discussions.
Moreover, we thank Pepe Márquez for discussions and support and Julian Kimmig for feedback on the web app. 
In addition, we acknowledge support from Sandeep Kumar with an initial prototype of the web app.
We thank Bastian Rieck for developing the \LaTeX-credit package (\url{https://github.com/Pseudomanifold/latex-credits}) and thank Berend Smit and Pepe Márquez for feedback on an early version of the manuscript.

>>>>

In this work, we report a novel benchmarking framework  (\Cref{fig:overview_figure}), which we call \chembench, and use it to reveal limitations of current frontier models for use in the chemical sciences.
Our benchmark consists of \variable{output/total_number_of_questions.txt}\xspace question-answer pairs compiled from diverse sources (\variable{output/manually_generated.txt}\xspace manually generated, and \variable{output/automatically_generated.txt}\xspace automatically generated).  
Our corpus covers a large fraction of the topics taught in undergraduate and graduate chemistry curricula. It can be used to evaluate any system that can return text (i.e., including tool-augmented systems).

@@

\paragraph{Judging chemical preference}

One interesting finding of recent research is that foundation models can judge interestingness.\autocite{zhang2024omniopenendednessmodelshuman}
If models could do so for chemical compounds, this would open opportunities for novel optimization approaches. 
Such open-ended tasks, however, depend on an external observer defining what interestingness is.\autocite{hughes2024openendednessessentialartificialsuperhuman}
Here, we posed models the same question~\textcite{Choung_2023} asked chemists at a drug company: \enquote{Which of the two compounds do you prefer?} (in the context of an early virtual screening campaign setting).
While chemists showed a fair degree of interrater agreement, most of our models do not correlate with the preferences of expert chemists---even if they perform well on many other tasks in \chembench.
This indicates that using preference tuning for chemical settings is a promising approach to explore in future research.

@@

In addition, we thank the OpenBioML.org community and their ChemNLP project team for valuable discussions.
Moreover, we thank Pepe Márquez for discussions and support and Julian Kimmig for feedback on the web app. 
In addition, we acknowledge support from Sandeep Kumar with an initial prototype of the web app.
We thank Bastian Rieck for developing the \LaTeX-credit package (\url{https://github.com/Pseudomanifold/latex-credits}) and thank Berend Smit for feedback on an early version of the manuscript.
